% !TEX encoding = UTF-8 Unicode
\documentclass[10pt,usepdftitle=false,aspectratio=169]{beamer}
\usepackage[left]{muibkitsec}
\usepackage{listings}

\usepackage{microtype}
\usepackage{graphbox}
\usepackage{booktabs} 

\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{algorithmic}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{diagbox}
\usepackage{float, multirow}
\usepackage{tikz, pgfplots}
\usepackage{tikzsymbols}
\usetikzlibrary{spy}
\usepackage{subcaption}
\usepgfplotslibrary{groupplots}
\pgfplotsset{compat=newest}

% ------------------------------------------------------------------------
\title{Adversarial Label Flips}
%\subtitle{modified new beamer template}
\author{Matthias Dellago \& Maximilian Samsinger}
\date{22 January 2021}

% ------------------------------------------------------------------------

\begin{document}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\begin{frame}[plain]
	\maketitle
\end{frame}	

\begin{frame}[fragile]
	\frametitle{Introduction}
	Summarize what \#5 is about and recap what the students need to know. (Maybe needs an extra slide)
	Explain (or visualize?) confusion matrix.
\end{frame}

\begin{frame}[fragile]
	\frametitle{Hypothesis}
	\begin{columns}
		\begin{column}{.5\columnwidth}
			\begin{block}{Research question}
				Does a relationship between ground truth and final predicted label exist given an untargeted attack?
			\end{block}
			\begin{block}{First question}
				Does a relationship exist \textit{at all}.
			\end{block}
		\end{column}
		\begin{column}{.5\columnwidth}
			\begin{alertblock}{Null hypothesis}
				The final predicted label is randomly (uniform) drawn from the set of all other labels.
			\end{alertblock}
			\begin{block}{Alternative hypothesis}
				The final predicted label is not randomly (uniform) drawn from the set of all other labels.
			\end{block}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}[fragile]
	\frametitle{Methods}
		\begin{block}{Datasets}
			MNIST, Fashion MNIST, CIFAR-10
		\end{block}
		\begin{alertblock}{Alert block}
			ResNet-18 for CIFAR-10.
			Some simple convolutional neural network for MNIST \& Fashion MNIST.
		\end{alertblock}
		\begin{alertblock}{Attacks}
			FGSM and PGD
		\end{alertblock}

\end{frame}

\begin{frame}[fragile]
	\frametitle{Stretch goals}
	\begin{enumerate}
		\item Study natural adversarial examples
		\item Looking for applications
		\item More attacks and/or architectures
	\end{enumerate}
\end{frame}

\begin{frame}[fragile]
	\frametitle{Brainstorming slide (will be removed)}
	\begin{columns}
		\begin{column}{.5\columnwidth}
			\begin{alertblock}{What do you want to achieve till the end of semester?}
				\begin{enumerate}
					\item Investigate relationship between ground truth labels and predicted label of adversarial examples. (Maybe formulate as null hyposisis: No correlation)
					\item Github repo for reproducibility.
					\item Max. Learn PyTorch
					\item Matthias. Learn ML  
				\end{enumerate}
			\end{alertblock}
		\end{column}
		\begin{column}{.5\columnwidth}
			\begin{block}{Why is your topic relevant?}
				Contribution to basic research. 
			\end{block}
			\begin{alertblock}{Stretch goals}
			More models/architectures.
			Influence of adversarial training.
			\end{alertblock}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}[fragile]
	\frametitle{Example Slide}
	\begin{columns}
		\begin{column}{.5\columnwidth}
			\begin{block}{Null hypothesis}
				Adversarial examples
			\end{block}
			\begin{alertblock}{Alert block}
				This is a alertblock
			\end{alertblock}
		\end{column}
		\begin{column}{.5\columnwidth}
			\begin{exampleblock}{Example block}
				Examples show up one by one$\dots$.
				\begin{itemize}
					\visible<1->{\item Example 1}
					\visible<2->{\item Example 2}
					\visible<3->{\item Example 3}
				\end{itemize}
			\end{exampleblock}
		\end{column}
	\end{columns}
\end{frame}


\end{document}
